Description of the power system model \emph{medea}

### 2019-08-01 doc/mathematical_description.tex
improved model description

\usepackage{natbib}
\usepackage{makecell}
\usepackage{eurosym} 
\usepackage[version=4]{mhchem}
%\usepackage{courier} 
\usepackage[inner=2.5cm,outer=2.5cm]{geometry}

\title{Description of the power system model \emph{medea}}
%\title{Mathematical description of the power system model \emph{medea}}
\date{\today}
\author{Sebastian Wehrle\thanks{Over recent years, \emph{medea} has grown into its current state thanks to inspiration and contributions from many friends and colleagues. 
In particular, I'd like to thank Johannes Schmidt, who contributed significant parts of the model code, for getting \emph{medea} started and for keeping us running; Dieter Mayr and Stefan Höltinger for early contributions; Peter Regener for inspiration and endurance with all things programming. Current work on \emph{medea} is funded through grateful support from the European Research Council ("reFUEL" ERC-2017-STG 758149)} \\University of Natural Resources and Life Sciences, Vienna}

>>>>

\usepackage{natbib}
\usepackage{makecell}
\usepackage{eurosym} 
\usepackage[version=4]{mhchem}
%\usepackage{courier} 
\usepackage[inner=2.5cm,outer=2.5cm, bottom=3cm]{geometry}

\title{Description of the power system model \emph{medea}}
%\title{Mathematical description of the power system model \emph{medea}}
\date{\today}
\author{Sebastian Wehrle\thanks{Over recent years, \emph{medea} has grown into its current state thanks to inspiration and contributions from many friends and colleagues. 
In particular, I'd like to thank Johannes Schmidt, who contributed substantial parts of the initial model code, for getting \emph{medea} started and for keeping us running; Dieter Mayr and Stefan Höltinger for early contributions; Peter Regener for inspiration and endurance with all things programming. Current work on \emph{medea} is funded through grateful support from the European Research Council ("reFUEL" ERC-2017-STG 758149)} \\University of Natural Resources and Life Sciences, Vienna}
